\speculake: Hiding Malware in Speculative Execution

### 2018-05-08 paper/figures.tex
fixup figure

\newcommand{\FigGeneralModel}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.4\textwidth]{figures/general_model.pdf}
    \caption{ General model of speculative computation within the Measure 
        process when triggered. \textit{Speculative Computation} has access
        to all variables which do not require a memory transaction within
        the current state of the process. The process can subsequently make
        \textit{Resultant Computations} based on the value returned from 
        \texttt{Flush+Reload} to update the state of the process. }
    \label{fig:general_model}
\end{figure}
}

>>>>

\newcommand{\FigGeneralModel}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.4\textwidth]{figures/general_model.pdf}
    \caption{ General model of speculative computation within the Payload 
        process when triggered. \textit{Speculative Computation} has read-only
        access to all memory within the process, and returns a result via a
        cache side channel (via the \texttt{probe\_array}).
        The process can subsequently make
        \textit{Resultant Computations} based on the value returned from
        the cache side channel to update the state of the process. }
    \label{fig:general_model}
\end{figure}
}
